### 2013-03-01 eusflat2013/preliminaries.tex
eusflat2013 new version

Several ill-known constraints can be aggregated by using boolean operators: and ($\wedge$), or ($\vee$), not ($\neg$). The possibility and neccesity for these operators are computed as follows.

@@

 \begin{figure}[h]
   \centering
   \includegraphics[scale=1.5]{graphs/ill-known-ti.eps}
   \caption{An ill-known time interval $J = \left[X, Y  \right]$ given by two ill-known values. }
   \label{fig:ill-known-ti}
 \end{figure}

An ill-known time interval is defined by two ill-known values (see Figure \ref{fig:ill-known-ti}). Therefore, both starting and ending points are not precissely known. The following is the notation for an ill-known time interval.

@@

Where both $X$ and $Y$ are ill-known time values.

The Allen's Relations between a crisp time interval $I = [a,b]$ ($a, b$ are crisp time points) and an ill-known time interval given by $J = [X,Y]$ ($X, Y$ are ill-known values, see Definition \ref{def:ill-known-value}) can be defined by using aggregations of ill-known constraints. Table \ref{tab:allen-relations} shows the corresponding ill-known constraints for each Allen's Relation. These ill-known constraints are aggregated by using the equations \eqref{and-ill-known-pos} to \eqref{not-ill-known-nec}.

>>>>

Several ill-known constraints can be aggregated by using the possibilistic extension of boolean operators: and ($\wedge$), or ($\vee$), not ($\neg$). The possibility and neccesity for these operators are computed as follows.

@@

 \begin{figure}[h]
   \centering
   \includegraphics[scale=1.5]{graphs/ill-known-ti.eps}
   \caption{An ill-known time interval IKTI $J = \left[X, Y  \right]$ given by two ill-known values. }
   \label{fig:ill-known-ti}
 \end{figure}

\begin{definition}
An ill-known time interval \emph{(IKTI)} is defined by two ill-known values (see Figure \ref{fig:ill-known-ti}). Therefore, both starting and ending points are not precissely known. The following is the notation for an IKTI.

@@

Where both $X$ and $Y$ are ill-known time values.
\end{definition}

The Allen's Relations between a crisp time interval $I = [a,b]$ ($a, b$ are crisp time points) and an IKTI given by $J = [X,Y]$ ($X, Y$ are ill-known values, see Definition \ref{def:ill-known-value}) can be defined by using aggregations of ill-known constraints. Table \ref{tab:allen-relations} shows the corresponding ill-known constraints for each Allen's Relation. These ill-known constraints are aggregated by using the equations \eqref{and-ill-known-pos} to \eqref{not-ill-known-nec}.

### 2013-03-01 eusflat2013/proposal.tex
eusflat2013 new version

\subsection{\label{subsec:sim-dif}Similarities and differences}

>>>>

Two frameworks for dealing with uncertainty in time intervals have been presented. In this section, we will study the equivalences between an uncertain time interval (UTI) and an ill-known time interval (IKTI). Nevertheless, there are some diferences in the semantics of UTIs and IKTIs which are also explained. Next to that, the computation of the Allen's Relations are compared.

\subsection{\label{subsec:sim-dif}Similarities and differences}
A time interval is defined by a starting and an ending point. When uncertainty arises, in one or both starting and / or ending points, then either an UTI $\pi_I$ or an IKTI can be used.

\begin{itemize}
 \item An IKTI $J = \left[X, Y \right]$ is defined by two ill-known values $X, Y$ which are respectively, the starting and ending points of the time interval. Two possibility distributions $\pi_X, \pi_Y$ are defined for $X$ and $Y$ respectively.
\item An UTI $\pi_I$ is defined by two possibility distributions, $\pi_S$, $\pi_E$ for the starting  and ending point respectively.
\end{itemize}

In the following, we will assume that:

\begin{align}
\pi_X &= \pi_S = \mu_S \\
\pi_Y &= \pi_E = \mu_E
\end{align}

Where $\mu_S, \mu_E$ are triangular membership functions. Notice that the main diference between an UTI and an IKTI is a matter of interpretation. IKTIs  keep both possibility distributions for both starting and ending poins, while UTIs take a t-norm (the minimum) of both possibility distributions (see Eq. \eqref{eq:possibility-uti}). That is, not all the crisp intervals between the boundaries of the starting and ending point are candidate intervals for the UTI.

\begin{figure}[h]
   \centering
   \includegraphics[scale=1.5]{graphs/equivalences.eps}
   \caption{Possibility degrees for two candidate intervals with respect to the UTI $\pi_I$. The upper crisp time interval has a possibility degree of 1, whereas the lower crisp interval has a possibility degree of 0. }
   \label{fig:ikc-greater}
 \end{figure}

It is possible to obtain the same interpretation for an IKTI, but some ill-known constraints must be defined over the starting and ending ill-known values $X$, $Y$. In \cite{Pons2011}, two constraints are defined to determinte whether a crisp time interval $[a, b]$ resides between the boundaries of $J$. In this case, all the crisp intervals whose boundaries are within the boundaries of $X$ and $Y$ are considered to be a candidate interval. Nevertheless, if we want to obtain the same interpretation as in the UTI, the following two ill-known constraints must be defined:

\begin{align}
 \label{eq:ikc-ikti-uti}
C_1 &\triangleq \left(=, X \right) \\
C_2 &\triangleq \left(=, Y \right)\\
\Pos \left(\left[a, b\right] \right) &= C_1 \left(a \right) \wedge C_2\left(b \right) =\\
\label{eq:equivalence-ikti-uti}
\Pos \left(\left[a, b\right] \right) &= \min \left( \pi_X(a), \pi_Y(b) \right)
\end{align}

In this case, Eq. \eqref{eq:equivalence-ikti-uti} is equivalent to Eq. \eqref{eq:possibility-uti}.
In the following subsection, we will study the connection between the Allen's relations in each framework.

\subsection{\label{subsec:eval-allen-relations}Evaluation of the Allen's Relations}
